Graphs

### 2018-11-08 analysis/index.Rmd
Moved around some of the files, and revising the home page.

1. [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)

2. [Comparison of signal denoising methods in Gaussian-distributed data
   sets.](gaussian.mean.est.html)

3. [Application of SMASH to motorcycle acceleration data.](motorcycle.html)

4. [Application of SMASH to ChIP-seq data.](chipseq.html)

>>>>

+ [**Illustration:** SMASH applied to the "spikes"
data set.](spikesdemo.html)

+ **Comparisons of signal denoising methods in simulated data:**

   - [Estimating the mean signal from Gaussian-distributed
      data.](gausshomo.html)
   - Estimating the variance function from Gaussian-distributed data.
   - Poisson-distributed data.

+ **Illustrative applications:**

   - [Motorcycle acceleration data.](motorcycle.html)
   - [ChIP-seq data.](chipseq.html)

### 2018-11-08 analysis/shiny.Rmd
Moved around some of the files, and revising the home page.

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("../../dsc/results/res.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))

>>>>

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("../output/gaus-dscr.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))
